

% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage{standalone}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{hyperref}
%  \usepackage{mathptmx}   % uncommenting this will change the font
\usepackage[11pt]{moresize}
\usepackage{url}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\begin{document}

\name{Ganindu Nanayakkara\\[12pt]} % the \\[12pt] adds a blank line after name



%\url{ganindu@cs.ait.ac.th}

\address{{\bf Address} \\
RDM Group / Aurrigo Driverless Technologies\\
No.33, Bilton Industrial Estate \\
Coventry, CV3 1JL \\
United Kingdom \\
%\url{st2000278@ait.asia} \\
\url{ganindu@aurrigo.com} }

\address{{\bf Home Address} \\
15, Hockett Street, \\
Coventry, CV3 5FR\\
United Kingdom. \\ % , 81280       // if I want to add the post code
\url{ganindu@gmail.com} \\
mobile: +447479607774 \\
%home: +(94)41 22 45 369
}





\begin{resume}

\section{Objective}

% Application for the Position of {\bf On the Job Trainee Engineer } at Sri
% Lankan Airlines.
 	    %Reference for my LinkedIn profile Just in case!! 
%  	    For Reference by Dr Tom Richardson, University of Bristol Robotics
%  	    laboratory 
Looking for new opportunities in autonomous vehicles/robotics research and development
% 		Engineer at Tesla as a fresh graduate to accept challenges and be part of the
% 		team that changed the course of space technology or simply because I have been
% 		a faithful SpaceX and Tesla fan for so long(even in the hard times).. 
%{\bf SpaceX} as a fresh graduate willing to accept challenges and be a part
% of the force that drives the company which my inspiration.

% \section{Information}
% %\begin{center}
% \begin{tabular}{ l  l  l }
% %   %  \hline
% %     \address{21 Bridge Street \\ Smallville \\ Dunwich DU3 4WE}  & hhjiij
% % & kk \\  % \hline
% Gender & \space & $Male$  \\ %\hline

% 
% 
% \end{tabular}
% %\end{center}

\section{Education}

B.S. in Mechatronics Engineering , Asian Institute of Technology, Thailand
(July 2014).


\section{Experience}

% things I do for Aurrigo
{\bf Present : Autonomous Vehicle Navigation and Control Systems Development Engineer.}
\\ 
\hfill  July 2017 

\begin{itemize} \itemsep -2pt  
\item Member of the Autonomous Control System Team at {\bf Aurrigo Driverless Technologies}\\
\url{https://aurrigo.com/}
\item Involved in Low Speed Autonomous Vehicle development.
\end{itemize}
\section{}
Currently working on developing Navigation and Control systems, Bayesian Filters, ROS Drivers, test-level safety supervisor alertness and sensor state  monitoring tools for autonomous vehicles.    

\underline{Highlights:} Control systems, Autonomous Local Navigation, Communications, Diagnostics, Testing and Development. 

% things I did in Cov Uni Part 2
{\bf Past 1.2: Research Assistant: {\bf Vehicle development},}
\\ 
\hfill  Nov 2015 - July 2017

\begin{itemize} \itemsep -2pt  % reduce space between..
% items
\item Member of the Team at {\bf Microcab Industries}\\
\url{http://www.microcab.co.uk}
\item Involved in Electric, H2E Prototype vehicle development.
\end{itemize}
\section{}
Worked on the development of Hydrogen Fuel Cell system state monitoring and diagnostics system. From concept, deign prototype to a design that was set to go on the whole fleet of SWARM 
Hydrogen Fuel Cell Electric Vehicles. Worked on a Renault Twizy(For Coventry University Future Vehicle Laboratory) H2EV conversion by working out how the Twizy woked with it's powertrain. Did Battery testing and pack assembly for microcab prototype vehicles. 

\underline{Highlights:} VCU development, Embedded Systems, Simulation, Safety
Cases.


% things I did in Cov Uni Part 1
{\bf Past 1.1: Research Assistant: {\bf Advanced Hybrid Powertrain
Development},}
\\ 
\hfill  Dec 2014 - July 2017
\begin{itemize} \itemsep -2pt  % reduce space between  items
\item Member of the Control and Sensor development team of the {\bf GKN
GyroDrive} a former {\bf Williams Hybrid} prototype development.
\end{itemize}


% brief on some stuff before going to work on H2EVs
\section{}
Developed sensor solutions for a high speed KERS rotor that was being developed for commercial applications. An optimal method was purposed after modeling the required behaviour and translating that to a prototype rig. Multiple methods including ones that does not require sensors at rotor level were considered.   

\underline{Highlights:} Motohawk Controller, Embedded Systems, Optimizing,
Project work, Safety, Simulation, Testing, Smart sensor development, MKX
Flywheel Energy Storage.

{\bf Trainee Engineer,} Camoplast Solideal, Midigama, Sri Lanka (3m).
\hfill Summer 2012 

\begin{itemize} \itemsep -2pt  % reduce space between..
% items
\item Carried out preventive maintenance in the {\bf Air Tyre} division.
\item Did Troubleshooting in tyre curing oven lines and general
\textit{\bf Air Tyre} machinery.
\item Supervised the power line installment for a 6kV mixer from installing the
Transformer to the installment of the machine.
\item Supervised the installation of a refurbished roller mill control system.
\end{itemize}
\underline{Highlights:} Co-operate environment, Working with
technicians, On the spot troubleshooting, Project work, Factory safety,
Leadership training program, Maintenance supervision, Parts ordering, Lean
manufacturing, ISO standards.


{\bf Research Assistant,} Mechatronics Laboratory, Chulalongkorn University,
Thailand. \\ \phantom \hfill  \hfill Summer 2013 \\ Mentored by:
Dr.
Ratchatin Chancharoen.
\begin{itemize}
  \itemsep -2pt %reduce space between items
  \item Development of a FPGA/CPLD based controller for a
  FANUC\textsuperscript{{\ssmall\texttrademark}} robot.
  \item Assisting graduate students to set up ROS in the Asctec Pelican
  Quad.
  \item Partnered in the designing, building and deployment of a Mechanum
  driven robot for the Thailand automation challenge,( worked in a ROS
  integration, application of the kinect sensor,development of the safety
  override). 
  \item[] Link to video: \url{http://www.youtube.com/watch?v=TE3Cqwn61A0}
  
  
\end{itemize}

\underline{Key areas:} ROS,
NI LabView\textsuperscript{\ssmall{\textregistered}},
Mecanum drive,
Matlab\textsuperscript{\ssmall{\textregistered}},
Simulink\textsuperscript{\ssmall{\textregistered}},
Vision, PCL, Embedded systems,
Microsoft\textsuperscript{\ssmall{\textregistered}} Kinect,
FANUC\textsuperscript{{\ssmall\texttrademark}},
3D printing.


\section{Capstone project}
{\bf Development of a Reconfigurable Ledge Climber}
\begin{itemize} \itemsep -2pt
  \item Conceptualized, designed, developed and implemented two modules of the
  class, modular reconfigurable robots.
  \item  Performed tasks of locomotion and ledge climbing.
  \item Analyzed the system response and behavioral characteristics and
  experimented on the performance and capabilities module wise.
  \item Experimented on multiple robot collaboration using the two modules
  to achieve the goals utilizing their capabilities and proved that the two robots
  can accomplish a task collaboratively which was previously impossible for a
  single module.
  \item[] Link to video: \url{http://www.youtube.com/watch?v=ny3iutQIQeU}
  
\end{itemize}
\underline{Key areas:}  Modular reconfigurable robotics, Multiple robot
collaboration, DC motor control, Control algorithms, Embedded systems, RF
communication.

\section{Areas of Interest}
\begin{itemize} \itemsep -2pt
  \item Control applications development, Autonomous navigation, 
        Drones/UAVs, AI.
  \item Sensor fusion, LQE, Inter Process Communication(IPC).
  \item Cloud robotics.
  \item Distributed systems, Swarm robotics/Multiple robot collaboration,
        Visual servoing.
  \item Formula1 Racing, Formula e Racing,  Electric Propulsion/Drivetrain.
  \item Rocketry, reusable space vehicles.
  \item Rapid prototyping.
  \item Exoskeletons.
  
\end{itemize}


\section{Academic \\ Projects \textit{(other)}}
\begin{itemize} \itemsep -2pt
  \item Obstacle avoiding robot,\textit{(built from scratch).}
  \item Stair climbing robot,\textit{remotely controlled,  for praxis}
  \item Design of a skeet launcher, \textit{Engineering mechanics.}
  \item Azimuth,\textit{(pneumatic powered projectile)} servo controlled
  turret\textit{, (targeting via vision, using the
  Matlab\textsuperscript{\textregistered} image processing toolbox was developed
  separately later.)}
  \item Detection of a virtual object by the Willow
  Garage\textsuperscript{{\ssmall\texttrademark}}  {\bf PR2} robot in Gazebo(ROS)
  simulator \textit{, Image processing class project.}
  \item Tracking objects using a native descriptor(designed by me) from the
  Microsoft\textsuperscript{\ssmall{\textregistered}} Kinect camera \textit{,
  Machine vision class project.}
  \item Design, developed and simulation of a traffic light system using PLC.
  \textit{Siemens S7.}
  \item Implementation of an Arduino ROS node \textit{, AIT Vision and Graphics
  Laboratory.}
  \item Partnering in a project using the Parrot.
  ARdrone\textsuperscript{\ssmall{\textregistered}}(ROS) for Human Detection
  in disaster situations by Haar-like fearure detection \textit{, AIT Vision and
  Graphics Laboratory.}
\end{itemize}

\section{Honors and Awards} {\bf Complimentary award} \\
The Mecanum project in support for the Chulalongkorn team in the
internship period received the award from MTEC in
the Thailand Automation Challenge. \\  \phantom \hfill \hfill December
2013

{\bf Sri Lanka Young Computer Scientist of the year award}
\begin{itemize} \itemsep -2pt
  \item Silver award: National.
  \item Gold colours: Best Hardware Design, National.
\end{itemize}
Received this project for the High school project of a secure gate and a blender
implemented using turbo pascal in the competition held by the ICT agency of
Sri Lanka({\bf ICTA}) and the Sri Lanka Association for the Software
Industry({\bf SLASI.})

\section{High School} St. Thomas' College Matara, Sri Lanka.


\section{Sports}
\begin{itemize} \itemsep -2pt
  \item Basketball: Represented the School $U17/U19$ Basketball teams and the
  Country for the AIT mini olympics.
  \item Chess: Represented the school chess team.
  \item Open water swimming\textit{(Sea)}: as a hobby \textit{Polhena Sri
  Lanka.}
  \item Surfing: as a hobby, \textit{Waligama, Midigama Sri lanka.}
  \item Mountain Biking and Hiking.
  \item Canoeing.
\end{itemize}

\section{Extra Curricular Activities}
\begin{itemize} \itemsep -2pt
  \item Co-Founder of the S. Thomas' College Electronics Bureau for Innovative
  Solutions({\bf EBIS.})
  \item Member of the 1\textsuperscript{st} Matara Scout Platoon.
  \item Member of the Young Inventors Club.
  \item Captain of the High School debating team.
  \item Matlab\textsuperscript{\ssmall{\textregistered}} community fellow.
  \url{http://www.mathworks.com/matlabcentral/fileexchange/authors/455468}
\end{itemize}

\section{High school Project} Experimental Project to determine the condition of
the water using operational amplifiers and the $PIC16f877A$
microcontroller, electronics implementation.

\section{familiar programing languages}
\begin{itemize} \itemsep -2pt
  \item C/C++/MicroC\textsuperscript{\ssmall{\textregistered}}/ASM
  \item
  Matlab\textsuperscript{\ssmall{\textregistered}}/
  Simulink\textsuperscript{\ssmall{\textregistered}}/Java/Python/Ladder/
  LabView\textsuperscript{\ssmall{\textregistered}}
\end{itemize}

\section{familiar Platforms and frameworks}
\begin{itemize} \itemsep -2pt
  \item Windows\textsuperscript{\ssmall{\textregistered}},
  Linux\textit{(Ubuntu)}, OSX\textsuperscript{\ssmall{\textregistered}}, ROS,
  Matlab\textsuperscript{\ssmall{\textregistered}}, LabView\textsuperscript{\ssmall{\textregistered}}
\end{itemize}

\section{Networking}
\begin{itemize} \itemsep -2pt
  \item \url{http://linkedin.com/in/ganindu}
  \item \url{https://twitter.com/ganindu}
  \item \url{https://www.facebook.com/ganindu}
\end{itemize}


% \begin{center}
%     \begin{tabular}{ l  l  l }
%   %  \hline
%        \address{21 Bridge Street \\ Smallville \\ Dunwich DU3 4WE}  & hhjiij  & kk \\  % \hline
%     $0.6K_c$ & $1.2K_c$  \\ %\hline
%     \end{tabular}
% \end{center}
\section{Referees}

\begin{ncolumn}{2}
\begin{itemize} \itemsep -3pt
  \item[] Jorge Barrio
  \item[] Senior Navigation Engineer
  \item[] Animal Dynamics Limited
  \item[] Oxford,
  \item[] United Kingdom
  \item[] \url{jorbarrio@gmail.com}
\end{itemize}
&
\begin{itemize} \itemsep -3pt
  \item[] Peter Jostins
  \item[] Associate Professor (Research), Institute for Future Transport and Cities
  \item[] \url{https://pureportal.coventry.ac.uk/en/persons/peter-jostins}
  \item[] \url{peter.jostins@coventry.ac.uk}
\end{itemize}
\end{ncolumn}

\begin{ncolumn}{2}
\begin{itemize} \itemsep -3pt
  \item[] Matthew N. Dailey
  \item[] Associate Professor
  \item[] Department of Computer Science and Information Management
  \item[] Asian Institute of Technology
  \item[] P.O. Box 4, Klong Luang,
  \item[] Pathumthani 12120 Thailand.
  \item[] +66 2 524 5712
  \item[] \url{mdailey@ait.ac.th}
  \item[] \url{http://www.cs.ait.ac.th/~mdailey}
\end{itemize}
&
\begin{itemize} \itemsep -3pt
  \item[] Ratchatin Chanchareon
  \item[] Associate Professor
  \item[] Department of Mechanical Engineering
  \item[] Chulalongkorn University
  \item[] 254 Phayathai Road, Pathumwan,
  \item[] Bangkok Thailand 10330.
  \item[] 66-(0)-2218-6643
  \item[] \url{ratchatin.c@chula.ac.th}
\end{itemize}
\end{ncolumn}

\begin{ncolumn}{2}
\begin{itemize} \itemsep -3pt
  \item[] Manukid Parnichkun
  \item[] Associate Professor
  \item[] Industrial Systems and Engineering
  \item[] School of Engineering and Technology
  \item[] Asian Institute of Technology
  \item[] P.O. Box 4, Klong Luang,
  \item[] Pathumthani 12120 Thailand.
  \item[] (662) 524 5229
  \item[] \url{manukid@ait.ac.th}
\end{itemize}
&
\begin{itemize} \itemsep -3pt
  \item[] A. M. Harsha S. Abeykoon, Ph.D
  \item[] Senior Lecturer
  \item[] B.Sc.Eng(Moratuwa),MSc(Keio),PhD(Keio).
  \item[] Department of Electrical Engineering
  \item[] University of Moratuwa,
  \item[] Moratuwa 10400 Sri Lanka.
  \item[] +94-11-2650301 ext. 3274
  \item[] \url{harsha@elect.mrt.ac.lk}
  \item[] \url{http://www.elect.mrt.ac.lk/harsha/}
\end{itemize}
\end{ncolumn}

\section{Declaration}{\bf I hereby certify that above particulars given are true
and correct to my best knowledge.} \\

\phantom \\
% {\bf\ldots\ldots\dots\dots\dots\dots\dots\dots}\\  % use this for dots
Yours Sincerely,\\
Ganindu Nanayakkara






%		creates a tabular environment with n equally
%		spaced columns.  Separate columns by & and
%		end them with \\

% \begin{minipage}{0.49\textwidth}
%
% \begin{itemize}
%   \item Assoc.Prof. Matthew N. Dailey \\
%         Asian Institute of Technology
%   \item Assoc.Prof Ratchatin Chanchroen \\
%         Chulalongkorn Unoversity
%
%
%
%
%  % \item second item
% \end{itemize}
% \end{minipage}%
% \hfill
% \begin{minipage}{0.45\textwidth}
% % \begin{tabular}{|p{\textwidth}}
%
% \begin{itemize}
% % $f(x) = 2x + 3y$ This line may go all along the end and wrap afterwards to the next as seen here\\
% % This is a forced next line by ending the previous line
% % % \end{tabular}
% \item[] Assoc.Prof. Matthew N. Dailey \\
%         Asian Institute of Technology
%   \item[] Assoc.Prof Ratchatin Chanchroe \\
%         Chulalongkorn University
%
% \end{itemize}
% \end{minipage}%

%  Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
%  \section{Computer \\ Skills}
%  \begin{tabular}{l p{3in}}
%  \underline{Languages:} & COBOL, Pascal,C, APL, Basic \\
%
%  \underline{Software:} &  SPIRES, dBase III, Datastar database
%  systems, GPSS simulation, FCS-EPS financial
% planning, SAS statistical analysis,
%  Lotus1-2-3, MPSX optimization modeling
%  \end{tabular}

\end{resume}
%\relax{Documant}
%\input{cover_letter}
\end{document}

% \include{cover_letter}

